\chapter{SYSTEM REQUIREMENTS SPECIFICATION}

\section{Introduction}
This chapter defines the functional and non-functional requirements for the My Task Manager application.

\section{Functional Requirements}

\subsection{Task Management}
\textbf{FR1: Add Task} - Allow users to create tasks with text description and optional date/time.

\textbf{FR2: View Tasks} - Display all tasks in organized, sorted list format.

\textbf{FR3: Complete Task} - Mark tasks as complete with visual feedback (strikethrough, reduced opacity).

\textbf{FR4: Delete Task} - Permanently remove tasks from the list.

\subsection{Task Organization}
\textbf{FR5: Automatic Sorting} - Sort tasks by completion status first, then by due date (earliest first).

\subsection{Data Persistence}
\textbf{FR8: Save Tasks} - Automatically save all tasks to localStorage after modifications.

\textbf{FR9: Load Tasks} - Retrieve saved tasks on application start.

\subsection{User Interface}
\textbf{FR10: Input Validation} - Validate that task text is not empty before creating tasks.

\textbf{FR11: Visual Feedback} - Provide clear visual indicators for task status.

\section{Non-Functional Requirements}

\subsection{Performance}
\textbf{NFR1: Response Time} - All operations complete within 100ms under normal conditions.

\textbf{NFR2: Storage Efficiency} - Support at least 1000 tasks within localStorage limits.

\textbf{NFR3: Scalability} - Maintain performance with up to 500 active tasks.

\subsection{Usability}
\textbf{NFR4: Ease of Use} - Usable without training; new users can add first task within 30 seconds.

\textbf{NFR5: Visual Design} - Attractive, modern interface with clear visual hierarchy.

\subsection{Reliability}
\textbf{NFR6: Data Integrity} - Maintain data integrity, preventing loss or corruption.

\textbf{NFR7: Error Handling} - Handle errors gracefully without crashing.

\subsection{Compatibility}
\textbf{NFR8: Browser Compatibility} - Function correctly on Chrome, Firefox, Edge, and Safari (version 90+).

\subsection{Security and Privacy}
\textbf{NFR9: Data Privacy} - Keep all user data local to device with no external requests.

\textbf{NFR10: Input Sanitization} - Sanitize user input to prevent security issues.

\subsection{Maintainability}
\textbf{NFR11: Code Quality} - Follow JavaScript best practices with clear documentation.

\section{System Constraints}
\begin{itemize}
\item Browser dependency (requires modern browser with localStorage)
\item Storage limit (constrained by browser localStorage, typically 5-10 MB)
\item Single device only (no synchronization)
\item JavaScript required
\item No backend infrastructure
\end{itemize}

\section{Hardware and Software Requirements}

\subsection{Minimum Requirements}
\begin{itemize}
\item Processor: 1 GHz or faster
\item RAM: 2 GB
\item Storage: 10 MB free space
\item Display: 1024x768 resolution
\item Browser: Chrome 90+, Firefox 88+, Edge 90+, or Safari 14+
\end{itemize}

\section{Use Case Scenarios}

\subsection{Use Case 1: Adding a Task}
User enters task text, optionally selects date/time, clicks Add Task. System validates, creates task, saves to localStorage, and displays in list.

\subsection{Use Case 2: Completing a Task}
User clicks Complete button. System toggles status, updates storage, re-renders list with visual changes (strikethrough, moved to bottom).

\section{Conclusion}
This chapter defined comprehensive requirements for the My Task Manager application, serving as the foundation for system design and implementation.
