\chapter{INTRODUCTION}

\section{Overview}
Task management is essential for personal and professional productivity. The My Task Manager application provides a simple, efficient, and user-friendly web-based solution for managing daily tasks without the complexity of commercial applications.

\section{Background}
Traditional task management methods like paper lists have limitations including lack of persistence and no automatic reminders. While digital tools emerged to address these issues, many suffer from complexity, privacy concerns, or internet dependency. This gap motivated the development of My Task Manager - a lightweight, browser-based application prioritizing simplicity and user privacy.

\section{Problem Statement}
The primary problem is: \textit{How can we create a simple, privacy-focused, offline-capable task management application that provides essential functionality without overwhelming users with complexity?}

\section{Objectives}
The primary objectives are:
\begin{enumerate}
\item Develop a functional task management system with CRUD operations
\item Implement data persistence using localStorage
\item Design an intuitive user interface requiring no training
\item Enable task scheduling with optional date/time
\item Provide clean and responsive user interface
\item Ensure code quality following best practices
\item Demonstrate web development proficiency
\end{enumerate}

\section{Scope of the Project}

\subsection{In Scope}
\begin{itemize}
\item Task creation, completion, and deletion
\item Optional date/time scheduling
\item Automatic task sorting
\item Data persistence using localStorage
\item Cross-browser compatibility
\end{itemize}

\subsection{Out of Scope}
\begin{itemize}
\item User authentication and multi-user support
\item Cloud synchronization
\item Task categories, tags, or priorities
\item Recurring tasks and subtasks
\item Mobile native applications
\item Backend server implementation
\end{itemize}

\section{Methodology}
The project follows a systematic approach: Requirements Analysis → System Design → Implementation → Testing → Documentation.

\textbf{Technologies:} HTML5, CSS3, JavaScript ES6+, localStorage API, DOM API

\section{Organization of the Report}
\textbf{Chapter 1} provides project overview and objectives.

\textbf{Chapter 2} reviews existing task management solutions and relevant technologies.

\textbf{Chapter 3} details functional and non-functional requirements.

\textbf{Chapter 4} presents system architecture and design diagrams.

\textbf{Chapter 5} discusses implementation and code structure.

\textbf{Chapter 6} describes testing strategies and results.

\textbf{Chapter 7} presents performance analysis and evaluation.

\textbf{Chapter 8} summarizes outcomes and future enhancements.
