% Developed by Suhasini Vijaykumar
\documentclass[12pt,a4paper,final,oneside]{report}
\usepackage{geometry}
\geometry{a4paper,total={170mm,257mm}}
\usepackage{amsmath,amssymb,amsfonts} 
\usepackage{graphics}
\usepackage{array}
\usepackage{url}
\usepackage[pdftex,breaklinks=true]{hyperref}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage[numbers]{natbib}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{lipsum}
\usepackage{setspace}
\renewcommand{\baselinestretch}{1.5} 
\usepackage[pdftex]{graphicx}
\usepackage{sidecap}

\usepackage{float}
\usepackage{placeins}
% Standard spacing configurations
\renewcommand{\baselinestretch}{1.5} 

% Relaxed float spacing to ensure images have breathing room
\setlength{\textfloatsep}{20pt plus 2.0pt minus 4.0pt}
\setlength{\intextsep}{20pt plus 2.0pt minus 4.0pt}
\setlength{\floatsep}{20pt plus 2.0pt minus 4.0pt}
\setlength{\abovecaptionskip}{10pt}
\setlength{\belowcaptionskip}{10pt}
\begin{document}


%\thispagestyle{empty}

\input{cover.tex}
\input{cert.tex}
\input{declaration.tex}
%\input{companyjoiningletter.tex}
\input{ack.tex}
\input{abst.tex}
 \addcontentsline{toc}{chapter}{Abstract}
%\clearpage
\tableofcontents
  \listoftables
   \addcontentsline{toc}{chapter}{List of Tables}
\listoffigures
  \addcontentsline{toc}{chapter}{List of Figures}
\input{nomenclature.tex}
\addcontentsline{toc}{chapter}{Nomenclature}
\newpage
\pagestyle{plain}
\pagenumbering{arabic}
%\singlespacing
%\onehalfspacing
\doublespacing
\pagestyle{fancy}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhf{}
\rhead{Task Manager}
\lfoot{BVIMIT}
\rfoot{Page \thepage}
\input{chap1.tex}
\input{chap2.tex}
\input{chap3.tex}
\input{chap4.tex}
\input{chap5.tex}
\input{chap6.tex}
\input{chap7.tex}
\input{chap8.tex}
\clearpage
\chapter*{References}
\addcontentsline{toc}{chapter}{References}
\thispagestyle{empty}

\sloppy
\begin{enumerate}
\item Mozilla Developer Network (MDN). (2024). \textit{HTML: HyperText Markup Language}. Retrieved from \url{https://developer.mozilla.org/en-US/docs/Web/HTML}

\item Mozilla Developer Network (MDN). (2024). \textit{CSS: Cascading Style Sheets}. Retrieved from \url{https://developer.mozilla.org/en-US/docs/Web/CSS}

\item Mozilla Developer Network (MDN). (2024). \textit{JavaScript Guide}. Retrieved from \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Guide}

\item Duckett, J. (2014). \textit{HTML and CSS: Design and Build Websites}. John Wiley \& Sons.

\item Duckett, J. (2014). \textit{JavaScript and JQuery: Interactive Front-End Web Development}. John Wiley \& Sons.

\item W3C. (2018). \textit{Web Content Accessibility Guidelines (WCAG) 2.1}. Retrieved from \url{https://www.w3.org/TR/WCAG21/}

\item Haverbeke, M. (2018). \textit{Eloquent JavaScript: A Modern Introduction to Programming}. No Starch Press.

\item Mozilla Developer Network (MDN). (2024). \textit{Web Storage API}. Retrieved from \url{https://developer.mozilla.org/en-US/docs/Web/API/Web\_Storage\_API}

\item Google Fonts. (2024). \textit{Google Fonts Documentation}. Retrieved from \url{https://developers.google.com/fonts}

\item Font Awesome. (2024). \textit{Font Awesome Icon Library}. Retrieved from \url{https://fontawesome.com/}
\end{enumerate}
\fussy


\end{document}




